Supporting Information

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
code added

>>>>

# 9. "Screening: institutional setting"
institutional <- q1_rob %>% 
  filter(setting == "Screening: institutional setting") %>%
  select(Study, D1, D2, D3, D4, D5, D6)
#Records: 21 studies

institutional_rob_trafficlight <- rob_traffic_light(data = institutional,
                                                    tool = "Generic",
                                                    psize = 10,
                                                    overall = FALSE)
p4 <- institutional_rob_trafficlight +
  ggplot2::labs(
    caption = " ") + 
  ggplot2::ggtitle("Screening: institutional setting") +
  ggplot2::theme(legend.position = "none")

# 10. "Screening: community setting"
communityset <- q1_rob %>% 
  filter(setting == "Screening: community setting") %>%
  select(Study, D1, D2, D3, D4, D5, D6)
#Records: 17 studies

communityset_rob_trafficlight <- rob_traffic_light(data = communityset,
                                                   tool = "Generic",
                                                   psize = 10,
                                                   overall = FALSE)

p5 <- communityset_rob_trafficlight +
  ggplot2::labs(
    caption = " ") + 
  ggplot2::ggtitle("Screening: community setting") +
  ggplot2::theme(legend.position = "none")

# 11. "Screening: occupational"
occupationalset <- q1_rob %>% 
  filter(setting == "Screening: occupational") %>%
  select(Study, D1, D2, D3, D4, D5, D6)
#Records: 12 studies

occupationalset_rob_trafficlight <- rob_traffic_light(data = occupationalset,
                                                      tool = "Generic",
                                                      psize = 10,
                                                      overall = FALSE)

p6 <- occupationalset_rob_trafficlight +
  ggplot2::labs(
    caption = "
    Domains:
  D1: Representativeness of the sample (selection bias)
  D2: Characteristics of non-respondents (selection bias)
  D3: Symptom assessment (information bias)
  D4: Recording of symptoms (information bias)
  D5: Classification of asymptomatic status (misclassification bias)
  D6: Selective reporting of symptoms status (attrition bias)")

p6 <- p6 + 
  ggplot2::ggtitle("Screening: occupational")

p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 1), ncol = 1, nrow = 3)
